YouPower -- A Social App for User Engagement in Power Grids

### 2015-12-14 SCITEPRESS_Conference_Latex/designConcept.tex
testing if the commit and push now work to the proper folder.
actions screenshots

This part of YouPower aims to provide users easy access to practical and inexpensive suggestions (or tips) to (1) increase energy awareness, (2) inform energy know-how, and to (3) shape their long-term behaviors related to household energy consumption.
% 
We collected about 50 suggestions (\url{https://goo.gl/R11QdZ}) from credible sources such as national and international energy agencies and associations. There are routine actions such as ``don't keep hot water flowing when you wash your dishes by hand'', regular actions such as ``defrost your fridge in $x$ days'', and one time actions such as ``install a programmable thermostat''.  
Each action is accompanied with a short explanation that mainly focuses on intrinsic values to target long-term sustainable behaviors, the estimated impact and entailed effort (on a scale of 1 to 5), and the information about how many users are taking the action.

@@

This part of YouPower is considered for households in the Stockholm test site. In Sweden, each apartment or house owner is a member of a housing cooperative that owns the property and annually elects a board that is in charge of the finances and maintenance of the property including making energy related decisions. 
Such a housing ownership concept exists in a number of EU and non-EU countries.
% 
Three main categories of features are designed for this part of YouPower: energy information about a user's own housing cooperative, energy information about other housing cooperatives, and support for communication between energy managers.
Primary users are energy managers and board members of housing cooperatives. Secondary users are ordinary cooperative members.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{"img/housing cooperatives 1"}
\includegraphics[width=0.9\linewidth]{"img/housing cooperatives 2"}
\caption{Mock-up of the ``housing cooperatives'' part}
\label{fig:brf}
\end{figure}

>>>>

\begin{figure*}[t!]
\centering
%\frame{\includegraphics[width=0.7\linewidth]{img/brf.pdf}}
\shadowimage[width=.296\linewidth]{img/action2.pdf}
\shadowimage[width=.296\linewidth]{img/action1.pdf}
\shadowimage[width=.298\linewidth]{img/action3.pdf}
\caption{Action suggestion part of YouPower}
\label{fig:action}
\end{figure*}

This part of YouPower (see screenshots in Figure \ref{fig:action}) aims to provide users easy access to practical and inexpensive suggestions (or tips) to (1) increase energy awareness, (2) inform energy know-how, and to (3) shape their long-term behaviors related to household energy consumption.
% 
We collected about 50 suggestions (\url{https://goo.gl/R11QdZ}) from credible sources such as national and international energy agencies and associations. There are routine actions such as ``don't keep hot water flowing when you wash your dishes by hand'', regular actions such as ``defrost your fridge in $x$ days'', and one time actions such as ``install a programmable thermostat''.  
Each action is accompanied with a short explanation that mainly focuses on intrinsic values to target long-term sustainable behaviors, the estimated impact and entailed effort (on a scale of 1 to 5), and the information about how many users are taking the action.

@@

This part of YouPower (see a screenshot in Figure~\ref{fig:brf}) is considered for households in the Stockholm test site. In Sweden, each apartment or house owner is a member of a housing cooperative that owns the property and annually elects a board that is in charge of the finances and maintenance of the property including making energy related decisions. 
Such a housing ownership concept exists in a number of EU and non-EU countries.

\begin{figure}[t!]
\centering
\shadowimage[width=.8\linewidth]{img/brf.pdf}
\caption{Housing cooperatives part of YouPower}
\label{fig:brf}
\end{figure}

% 
Three main categories of features are designed for this part of YouPower: energy information about a user's own housing cooperative, energy information about other housing cooperatives, and support for communication between energy managers.
Primary users are energy managers and board members of housing cooperatives. Secondary users are ordinary cooperative members.

@@
